Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-09-25 paper/appendix.tex
duration plot
a

\begin{figure}[t!]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_supp.pdf}
  \caption{}
  \label{fig:meg_supp}
\end{figure}

@@

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_supp.pdf}
  \caption{Average $\Delta R$ for each $Y$ dimension (Forward model), canonical components (PLS and CCA) or feature (B2B) across subjects. Formally, Backward model cannot have a $\Delta R$ because it never demix multiple $X$ features. In such cases, we thus simply report the decoding score.}
  \label{fig:meg_supp}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/duration}
  \caption{Wall-clock run-time for our method B2B and for the baselines. We see that B2B runs much faster than baselines. \label{fig:duration}}
\end{figure}
